\documentclass{article}

\usepackage{tabularx}
\usepackage{booktabs}

\title{Meeting Notes\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
2023/09/15 & Michael Kim & Creation of document and addition of meeting notes 2023/09/14 \\
2023/09/16 & Michael Kim & Adding meeting notes for 2023/09/16 \\
2023/09/18 & Michael Kim & Fixed spelling mistake\\
\bottomrule
\end{tabularx}
\end{table}

\section*{Meeting Notes 2023/09/14}

\subsection*{Attendance}
\begin{itemize}
\item Zihao Du 
\item Matthew Miller
\item Abhiram Neelamraju
\item Michael Kim
\end{itemize}
Firas notified that he was sick.

\subsection*{Meeting Summary}
\begin{itemize}
\item Discussed what other projects we are interested in, send 3 additional emails to interested projects.
\item Surveryed everone on our collective skill level and prior experience that would relate to the project.
\end{itemize}

\subsection*{Action Items}
\begin{itemize}
\item Contact other project supervisors and secure our project.
\item Discuss the rules of operation, assign roles for pull request review and other tasks.
\item Update all values and other fields in github
\end{itemize}

\section*{Meeting Notes 2023/09/16}

\subsection*{Attendance}
\begin{itemize}
\item Zihao Du 
\item Matthew Miller
\item Abhiram Neelamraju
\item Michael Kim
\item Firas Elayan
\end{itemize}

\subsection*{Meeting Summary}
\begin{itemize}
\item Discussed which projects out of the 5 we would like.
\item 13, 6, 17, 9, 16 priority; Zihao will contact the remaining professors for the meeting.
\item Will discuss the GitHub rules of collaboration at later meeting due to time constraints.
\end{itemize}

\subsection*{Action Items}
\begin{itemize}
\item Dr. Kolasa, Ecosystem (13): Meeting Monday 2:30~4:30, waiting for his reply (Michael, Abhiram)
\item John Peng, Smart Textbook (16): Meeting Tuesday, will cancel if we select project on Monday
\item Dr. Yang, ZMM GPU Fortran (9): Meeting Monday 10:30~11:15 (Michael, Matthew, Abhiram)
\item Dr. Yuan, XR Game (17): Discuss it post-lecture Monday
\item Dr. Greenberg, ChemFAST (6): Meeting 12:30~1:15 (Virtual)
\end{itemize}

Meeting minutes tracked in Issues from this point onwards.


\end{document}
